The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-02-07 Paper.Rmd
fixed a table reference link that was not working

dt <- tibble(Description = c("1. P-value, independence test",
           "2. Minimum-AIC copula",
           "3. AIC weight of minimum-AIC copula",
           "4. AIC weight of N copula",
           "5. P-value, Cramer-von Mises goodness of fit test",
           "6. P-value, Kolmogorov-Smirnov goodness of fit test",
           "7. Model averaged lower-tail dependence",
           "8. Model averaged upper-tail dependence",
           "9. Model averaged lower- minus upper-tail dependence",
           "10. Asymmetry rank in surrogates")
)
tab_bivar_summary<-cbind(dt,tab_bivar_summary)
knitr::kable(tab_bivar_summary, 
             format="latex",
             caption = "Summary of Q1 results for bivariate datasets. The $p$-values in rows 5-6 are for the minimum-AIC copula. Model averaging used for rows 7-9 was based on AIC weights. For row 10, the statistic $P_{0,0.1}-P_{0.9,1}$ was computed for real data and for 1000 Kendall-preserving surrogate datasets with N copulas, and the rank of real-data value in the distribution of surrogate values is presented. If ranks were $>975$ or $<25$, asymmetry of tail dependence was significant compared to a N-copula null hypothesis.",
             booktabs=T, linesep = "\\addlinespace",
             col.names = c(" ", "Soil C and N", "Bird masses and BMR", "Mammal masses and BMR", "Cedar Creek data")
             )%>%column_spec(2:5,width="1.4cm")%>%
             column_spec(1, width = "8.5cm")%>%kable_styling(latex_options = "basic",position = "center")
```
<!--***DAN: Shya, it says Pl-Pu above, but I suspect it was P_first slice - P_last slice, right?
Can you please look back at the code, if necessary, and write a comment below this one 
indicating what results are actually presented in the table?
***Shya: Yes, you are right, here Pl-Pu means P_first slice - P_last slice. In table, item 10 : Assymetry rank is shown for Kendall preserving surroagates.
Reference : bivfunctionplot.R file, lines 134,135,161
***DAN: OK, great. I have made changes to deal with this, but am leaving the comment for now
as a reminder that we looked at this-->

>>>>

dt <- tibble(Description = c("1. P-value, independence test",
           "2. Minimum-AIC copula",
           "3. AIC weight of minimum-AIC copula",
           "4. AIC weight of N copula",
           "5. P-value, Cramer-von Mises goodness of fit test",
           "6. P-value, Kolmogorov-Smirnov goodness of fit test",
           "7. Model averaged lower-tail dependence",
           "8. Model averaged upper-tail dependence",
           "9. Model averaged lower- minus upper-tail dependence",
           "10. Asymmetry rank in surrogates")
)
tab_bivar_summary<-cbind(dt,tab_bivar_summary)
knitr::kable(tab_bivar_summary, 
             format="latex",
             caption = "Summary of Q1 results for bivariate datasets. The $p$-values in rows 5-6 are for the minimum-AIC copula. Model averaging used for rows 7-9 was based on AIC weights. For row 10, the statistic $P_{0,0.1}-P_{0.9,1}$ was computed for real data and for 1000 Kendall-preserving surrogate datasets with N copulas, and the rank of real-data value in the distribution of surrogate values is presented. If ranks were $>975$ or $<25$, asymmetry of tail dependence was significant compared to a N-copula null hypothesis.\\label{tab_bivar_summary}",
             booktabs=T, linesep = "\\addlinespace",
             col.names = c(" ", "Soil C and N", "Bird masses and BMR", "Mammal masses and BMR", "Cedar Creek data")
             )%>%column_spec(2:5,width="1.4cm")%>%
             column_spec(1, width = "8.5cm")%>%kable_styling(latex_options = "basic",position = "center")
```
<!--***DAN: Shya, it says Pl-Pu above, but I suspect it was P_first slice - P_last slice, right?
Can you please look back at the code, if necessary, and write a comment below this one 
indicating what results are actually presented in the table?
***Shya: Yes, you are right, here Pl-Pu means P_first slice - P_last slice. In table, item 10 : Assymetry rank is shown for Kendall preserving surroagates.
Reference : bivfunctionplot.R file, lines 134,135,161
***DAN: OK, great. I have made changes to deal with this, but am leaving the comment for now
as a reminder that we looked at this-->
